COVID-19 Policy-Compliance in Europe

### 2020-12-26 Draft.Rmd
changed & to and

To assess our hypothesis more thoroughly, policy-compliance is additionally corrected for COVID-19-cases [@Data14DayNotification2020] and public attention on the topic, as approximated by Google search queries with the terms *"covid"* & *"coronavirus"* [@GoogleTrends].

>>>>

To assess our hypothesis more thoroughly, policy-compliance is additionally corrected for COVID-19-cases [@Data14DayNotification2020] and public attention on the topic, as approximated by Google search queries with the terms *"covid"* and *"corona"* [@GoogleTrends].
